A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-22 paper.tex
Acknowledgements
(2,1) done

\subsection*{Acknowledgements}
We would like to thank Owen Gwilliam, Justin Hilburn and Philsang Yoo for helpful discussions during the preparation of this paper.  
We are also grateful to Dylan Butson for kind discussion of his related forthcoming work, specifically in reference to supersymmetric theories in dimension $6$.  
The research of C.E. on this project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (QUASIFT grant agreement 677368).
The work of B.W. was supported by Northeastern University and National Science Foundation Award DMS-1645877.
\pavel{Support}

@@

\begin{prop}
\label{4d_donaldson_susy_prop}
Suppose $Q_t$ is the rank $(2,0)$ supercharge of \ref{eq:4dHodgefamily}.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
\begin{align*}
S_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
& + \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1}  + [a, \wt a])\chi^* + [\phi, \phi]\xi^* \right) \\
&+ \int\dvol\left( t\Omega^{-1} F_{2, 0}\wedge B^* + (t\dd_{A_{1, 0}} a, \rho^*)\right) \\
S^{(2)}_{\rm gauge} (Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^* B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
S_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varsigma, \phi^*) + [\phi, \nu] + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) + [\nu, a]\varsigma^* \right) \\
S_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
\end{align*}
\end{prop}
\brian{Anti field in $S^{(1)}_{matter}$.}
%The $(1,2)$ action is in comments, it should agree with the $t=0$ limit of the above.
%\begin{align*}
%I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varsigma, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varsigma^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
%&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varsigma^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
%I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
%\end{align*}

@@

Observe that the quadruple of fields $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ has the same Poisson brackets as the quadruple $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$. Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}. We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}. We are left with the action
\[S_{\mr{BF}} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
where $S_{\mr{BF}}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory. The former is given by (cf. the proof of Theorem \ref{thm:4d2holomorphictwist})
\[
\xymatrix@R=0.5cm@C=0cm{
\ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} & \ul{4} \\ 
& \Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
\Omega^0(\CC^2; \gg)_a  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b}  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*}  \ar@{-->}^{t\id}[ur] \\
& &  \Omega^{2,0}(\CC^2 ; \gg)_{B^*}  \ar@{-->}^{t\id}[dr] \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r]  \ar@{-->}^{t\id}[dr] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*}  \ar@{-->}^{t\id}[dr] \\
& & & \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
& & \Omega^0(\CC^2 ; U\otimes K^{1/2})_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U\otimes K^{1/2})_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U\otimes K^{1/2})_{\varsigma^*} \\
& \Omega^{2,0}(\CC^2 ; U\otimes K^{-1/2})_{\varsigma} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U\otimes K^{-1/2})_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U\otimes K^{-1/2})_{\phi^*}  \ar@{-->}^{t\id}[ur]
}
\]
which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
\end{proof}

@@

Let $S(s,t)$ be the action functional of the 4d $\cN=4$ super Yang--Mills theory twisted by $Q_0 + tQ_1 + sQ_2$. Then we have
\[S(s, t) = S(s, 0) + \left(S^{(1)}(tQ_1) + 2 S^{(2)}(Q_0, tQ_1) + S^{(2)}(tQ_1, tQ_1)\right) + 2S^{(2)}(tQ_1, sQ_2),\]
where $S^{(1)}, S^{(2)}$ are the supersymmetry actions from Section \ref{sect:gaugemultipletSUSY}. Here the middle three terms in the parentheses are the $t$-dependent terms in Proposition \ref{4d_donaldson_susy_prop} and $S^{(2)}(tQ_1, sQ_2)$ is proportional to $\tilde{\chi}^*$.

@@

\item Using Proposition \ref{prop:BRSTdoublet} we set $\tilde{a} = 0$, $\tilde{\chi}^*=0$ and $\tilde{\chi}+t\chi, \tilde{a}^*$ to certain values.

\item Using Proposition \ref{prop:BRSTdoublet} we set $\tilde{\nu}^* = 0$, $\nu = 0$ and $\tilde{\nu},\nu^*$ to certain values.
\end{itemize}
\end{proof}

\begin{proof}
Fix a rank $(2,1)$ supercharge of the form $Q_{s,t} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.  Consider the supersymmetry actions 
\begin{align*}
&I^{(1)}(Q_0 + tQ_1 + sQ_2) \\
&I^{(2)}(Q_0 + tQ_1 + sQ_2, Q_0 + tQ_1 + sQ_2).
\end{align*}
We will compute the corresponding $\ZZ$-graded $Q_{s,t}$-twisted theory.  Our strategy will be to realize the twisted BV action functional as the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist} plus a correction term, which we will identify as turning on the Hodge deformation.

We will make this identification by eliminating component fields from the correction term using the strategy of the proof of Theorem \ref{thm:4dDonaldsontwist}.  The correction in question is the sum
\begin{equation}
\label{eq:4d_12_general_def}
\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
\end{equation}
First let us observe that the final term, $I^{(2)}(tQ_1, sQ_2)$, is proportional to $st \wt \chi^*$, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $st (Q_1,\lambda^*)$, which is proportional to $st \wt \chi^*$.  This is important because in a moment we will be able to set $\wt \chi^* = 0$, so this term will vanish.

Now, we will make the same moves as in the proof of Theorem \ref{thm:4dDonaldsontwist} to eliminate component fields.  The key fact, which means that this procedure works, is that the part of the deformation of the action proportional to $s$, namely
\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
is a sum of terms that all involve both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi, \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).  That is, none of the summands involve only fields from the vector multiplet, or only fields from the hypermultiplet.  To be a little more precise we should say that the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.  In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.

So, in the proof of Theorem \ref{thm:4dDonaldsontwist}, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.  We then used Proposition \ref{prop:integrateoutfield} to eliminate the fields $\chi^*-t\wt\chi^*, \chi$.  The proposition still applies here, because the further twist by $sQ_2$ does not introduce a $\chi^2$ or $(\chi^*-t\wt\chi^*)^2$ term.  Finally, we used Proposition \ref{prop:BRSTdoublet} to eliminate the trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$.  Again, the proposition still applies here: each time we apply the proposition, we must only ensure that there are no terms in the twisted action proportional to a pair of fields $(X, Y)$, we need only observe that the deformation could not introduce terms to the action proportional to $XX^*$ or $YY^*$.

As a result of this argument, we are free, as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.  Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.  That is, we extract the summand in the $Q_{s,t}$-twisted action of the form $(\chi^* - t\wt \chi^*)S_1$.

It is important that we check that this expression $S_1$ occuring in the $Q_{s,t}$-twisted action functional is equal to the corresponding expression in the $Q_0 + sQ_2$-twisted action functional, so that the presence of our correction term does not alter the $Q_0 + sQ_2$-twisted action.  To see this, first recall that we argued above that there are no terms proportional to $st$ after setting $\wt \chi^* = 0$.  Then, look at terms proportional to $t \chi^*$ in equation \ref{4d_donaldson_susy_prop}.  Notice that all such terms are also proportional to $\wt \chi^*$, so vanish after setting $\wt \chi^* = 0$.

We have therefore shown that the $Q_{s,t}$-twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation \ref{eq:4d_12_general_def}.  The $st$-term vanishes, and the deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
\begin{equation}
\label{eq:4d_12_further_deformation}
t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right)
\end{equation}
in terms of the $\mr U(2)$-component fields, which can be further broken to $\spin(2;\RR) \times \spin(2;\RR)$.

Therefore, the $Q_{s,t}$ twisted action theory is equivalent to the rank $(1,1)$-twisted theory from Theorem \ref{thm:4d_11_twist}, with action deformed by the expression \ref{eq:4d_12_further_deformation}.  This deformation gives the desired theory.  The rank $(1,1)$-twisted theory was $\ZZ$-graded, and the deformation here by $tQ_1$ is a deformation by a degree 1 operator, so the twisted theory is also $\ZZ$-graded.  Finally, the rank $(1,1)$-twisted theory was shown to be $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and the deformation \ref{eq:4d_12_further_deformation} was $\MU(2)$-equivariant, so the rank $(2,1)$-twisted theory is still $\spin(2;\RR) \times \spin(2;\RR)$-invariant.
\end{proof}

>>>>

\subsection*{Acknowledgements}
We would like to thank Owen Gwilliam, Justin Hilburn and Philsang Yoo for helpful discussions during the preparation of this paper.  
We are also grateful to Dylan Butson for kind discussion of his related forthcoming work, specifically in reference to supersymmetric theories in dimension $6$.  
The research of C.E. on this project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (QUASIFT grant agreement 677368).
The research of P.S. was supported by the NCCR SwissMAP grant of the Swiss National Science Foundation.
The research of B.W. was supported by Northeastern University and National Science Foundation Award DMS-1645877.

@@

\begin{prop}
\label{4d_donaldson_susy_prop}
Suppose $Q_t$ is the rank $(2,0)$ supercharge of \ref{eq:4dHodgefamily}.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
\begin{align*}
S_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
& + \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1}  + [a, \wt a])\chi^* + [\phi, \phi]\xi^* \right) \\
&+ \int\dvol\left( t\Omega^{-1} F_{2, 0}\wedge B^* + (t\dd_{A_{1, 0}} a, \rho^*)\right) \\
S^{(2)}_{\rm gauge} (Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^* B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
S_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varsigma, \phi^*) + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) + [\nu, a]\varsigma^* \right) \\
S_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
\end{align*}
\end{prop}
%\brian{Anti field in $S^{(1)}_{matter}$.}
%The $(1,2)$ action is in comments, it should agree with the $t=0$ limit of the above.
%\begin{align*}
%I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varsigma, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varsigma^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
%&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varsigma^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
%I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
%\end{align*}

@@

Observe that the quadruple of fields $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ has the same Poisson brackets as the quadruple $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$. Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}. We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}. We are left with the action
\begin{equation}\label{eqn:(2,0)}
S_{\mr{BF}} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),
\end{equation}
where $S_{\mr{BF}}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory. The former is given by (cf. the proof of Theorem \ref{thm:4d2holomorphictwist})
\[
\xymatrix@R=0.5cm@C=0cm{
\ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} & \ul{4} \\ 
& \Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
\Omega^0(\CC^2; \gg)_a  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b}  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*}  \ar@{-->}^{t\id}[ur] \\
& &  \Omega^{2,0}(\CC^2 ; \gg)_{B^*}  \ar@{-->}^{t\id}[dr] \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r]  \ar@{-->}^{t\id}[dr] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*}  \ar@{-->}^{t\id}[dr] \\
& & & \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
& & \Omega^0(\CC^2 ; U\otimes K^{1/2})_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U\otimes K^{1/2})_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U\otimes K^{1/2})_{\varsigma^*} \\
& \Omega^{2,0}(\CC^2 ; U\otimes K^{-1/2})_{\varsigma} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U\otimes K^{-1/2})_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U\otimes K^{-1/2})_{\phi^*}  \ar@{-->}^{t\id}[ur]
}
\]
which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
\end{proof}

@@

Let $S(s,t)$ be the action functional of the 4d $\cN=4$ super Yang--Mills theory twisted by $Q_0 + tQ_1 + sQ_2$. Then we have
\begin{equation}\label{eqn:(2,1)2}
S(s, t) = S(s, 0) + \left(S^{(1)}(tQ_1) + 2 S^{(2)}(Q_0 + tQ_1) + S^{(2)}(tQ_1)\right) + 2S^{(2)}(tQ_1 + sQ_2),
\end{equation}
where $S^{(1)} = S^{(1)}_{\rm gauge}, S^{(2)} = S^{(2)}_{\rm gauge}$ are the functionals from Section \ref{sect:gaugemultipletSUSY} encoding the infinitesimal actions by supersymmtery. 
Here the middle three terms in the parentheses are the $t$-dependent terms in Proposition \ref{4d_donaldson_susy_prop} and $S^{(2)}(tQ_1, sQ_2)$ is proportional to $\tilde{\chi}^*$.

@@

\item Using Proposition \ref{prop:BRSTdoublet} we set $\Tilde{a} = 0$, $\tilde{\chi}^*=0$ and $\Tilde{\chi}+t\chi, \Tilde{a}^*$ to certain values.

\item Using Proposition \ref{prop:BRSTdoublet} we set $\Tilde{\nu}^* = 0$, $\nu = 0$ and $\Tilde{\nu},\nu^*$ to certain values.
\end{itemize}

The last term $S^{(2)}(tQ_1 + sQ_2)$ in Equation (\ref{eqn:(2,1)2}) is proportional to $\Tilde{\chi}^*$, therefore it disappears upon applying the third step above. 
Applying all the remaining steps, the first term $S(s,0)$ becomes the action functional of the $(1,1)$ twist upon setting $s=1$, see Theorem \ref{thm:4d4partialtwist}. 
Finally, the term in parentheses in Equation (\ref{eqn:(2,1)2}) agrees with the $t$-dependent terms of in Equation (\ref{eqn:(2,0)}), (accept now the fields are adjoint valued). 
We have already seen that the $t$-dependent terms give rise to the desired Hodge family, so this completes the proof. 
\end{proof}

%\begin{proof}
%Fix a rank $(2,1)$ supercharge of the form $Q_{s,t} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.  Consider the supersymmetry actions 
%\begin{align*}
%&I^{(1)}(Q_0 + tQ_1 + sQ_2) \\
%&I^{(2)}(Q_0 + tQ_1 + sQ_2, Q_0 + tQ_1 + sQ_2).
%\end{align*}
%We will compute the corresponding $\ZZ$-graded $Q_{s,t}$-twisted theory.  Our strategy will be to realize the twisted BV action functional as the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist} plus a correction term, which we will identify as turning on the Hodge deformation.
%
%We will make this identification by eliminating component fields from the correction term using the strategy of the proof of Theorem \ref{thm:4dDonaldsontwist}.  The correction in question is the sum
%\begin{equation}
%\label{eq:4d_12_general_def}
%\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
%\end{equation}
%First let us observe that the final term, $I^{(2)}(tQ_1, sQ_2)$, is proportional to $st \wt \chi^*$, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $st (Q_1,\lambda^*)$, which is proportional to $st \wt \chi^*$.  This is important because in a moment we will be able to set $\wt \chi^* = 0$, so this term will vanish.
%
%Now, we will make the same moves as in the proof of Theorem \ref{thm:4dDonaldsontwist} to eliminate component fields.  The key fact, which means that this procedure works, is that the part of the deformation of the action proportional to $s$, namely
%\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
%is a sum of terms that all involve both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi, \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).  That is, none of the summands involve only fields from the vector multiplet, or only fields from the hypermultiplet.  To be a little more precise we should say that the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.  In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.
%
%So, in the proof of Theorem \ref{thm:4dDonaldsontwist}, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.  We then used Proposition \ref{prop:integrateoutfield} to eliminate the fields $\chi^*-t\wt\chi^*, \chi$.  The proposition still applies here, because the further twist by $sQ_2$ does not introduce a $\chi^2$ or $(\chi^*-t\wt\chi^*)^2$ term.  Finally, we used Proposition \ref{prop:BRSTdoublet} to eliminate the trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$.  Again, the proposition still applies here: each time we apply the proposition, we must only ensure that there are no terms in the twisted action proportional to a pair of fields $(X, Y)$, we need only observe that the deformation could not introduce terms to the action proportional to $XX^*$ or $YY^*$.
%
%As a result of this argument, we are free, as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.  Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.  That is, we extract the summand in the $Q_{s,t}$-twisted action of the form $(\chi^* - t\wt \chi^*)S_1$.  
%
%It is important that we check that this expression $S_1$ occuring in the $Q_{s,t}$-twisted action functional is equal to the corresponding expression in the $Q_0 + sQ_2$-twisted action functional, so that the presence of our correction term does not alter the $Q_0 + sQ_2$-twisted action.  To see this, first recall that we argued above that there are no terms proportional to $st$ after setting $\wt \chi^* = 0$.  Then, look at terms proportional to $t \chi^*$ in equation \ref{4d_donaldson_susy_prop}.  Notice that all such terms are also proportional to $\wt \chi^*$, so vanish after setting $\wt \chi^* = 0$.
%
%We have therefore shown that the $Q_{s,t}$-twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation \ref{eq:4d_12_general_def}.  The $st$-term vanishes, and the deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
%\begin{equation}
%\label{eq:4d_12_further_deformation}
%t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right)
%\end{equation}
%in terms of the $\mr U(2)$-component fields, which can be further broken to $\spin(2;\RR) \times \spin(2;\RR)$.
%
%Therefore, the $Q_{s,t}$ twisted action theory is equivalent to the rank $(1,1)$-twisted theory from Theorem \ref{thm:4d_11_twist}, with action deformed by the expression \ref{eq:4d_12_further_deformation}.  This deformation gives the desired theory.  The rank $(1,1)$-twisted theory was $\ZZ$-graded, and the deformation here by $tQ_1$ is a deformation by a degree 1 operator, so the twisted theory is also $\ZZ$-graded.  Finally, the rank $(1,1)$-twisted theory was shown to be $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and the deformation \ref{eq:4d_12_further_deformation} was $\MU(2)$-equivariant, so the rank $(2,1)$-twisted theory is still $\spin(2;\RR) \times \spin(2;\RR)$-invariant.
%\end{proof}
